---
title: "Writeup"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    highlight: tango
    theme: sandstone
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

link to dataset: https://www.kaggle.com/datasets/kundanbedmutha/hotel-booking-reservation

# Step 0 - Why?


image

explain hotel cancellation

allow overbooking to minimize damage



```{r}
df <- read.csv("data/hotel_cleaned.csv")
library(ggplot2)

ggplot(df, aes(x = is_canceled)) +
  geom_bar() +
  labs(title = "Distribution of Cancellation",
       x = "Cancellation (0 = No, 1 = Yes)",
       y = "Count")
```

There is quite a high cancellation rate. Thus, it is worth investigating how much we should allow overbooking.

# Step 1&2&3: Load, Clean, and Split Data

Refer to the *data_cleaning_splitting.Rmd* under the data folder.



## Step 4&5: Create, Predict Models

source("...")

### Logistic Regression





### KNN








### ANN











### SVM











### Decision Tree











### Random Forest





## Step 6: Combine Models


with cost matrix

without cost matrix






## Step 7: Final Prediction




## Step 8: Model Evaluation




## Step 9: Implications, Limitations, and Further Steps



